Supporting Information

### 2021-10-08 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
Everything added

@@

![ROB Q1_1](q1_1_new.png)
![ROB Q1_1](q1_2_new.png)

>>>>

###ROB analysis for Q2.1
q2_rob <- df_rob %>%
  filter(!is.na(rob_1)) %>%
  filter(record_id != 122) %>%
  filter(q3_sar == 1)  %>%
  select(authoryear, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6) %>%
  rename(Study = authoryear, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
         D5 = rob_5, D6 = rob_6)

q2_rob$D1 <- ifelse(q2_rob$D1 == 1, "High", ifelse(q2_rob$D1 == 2, "Unclear", "Low"))
q2_rob$D2 <- ifelse(q2_rob$D2 == 1, "High", ifelse(q2_rob$D2 == 2, "Unclear", "Low"))
q2_rob$D3 <- ifelse(q2_rob$D3 == 1, "High", ifelse(q2_rob$D3 == 2, "Unclear", "Low"))
q2_rob$D4 <- ifelse(q2_rob$D4 == 1, "High", ifelse(q2_rob$D4 == 2, "Unclear", "Low"))
q2_rob$D5 <- ifelse(q2_rob$D5 == 1, "High", ifelse(q2_rob$D5 == 2, "Unclear", "Low"))
q2_rob$D6 <- ifelse(q2_rob$D6 == 1, "High", ifelse(q2_rob$D6 == 2, "Unclear", "Low"))

q2_plot_ds <- q2_rob %>% 
  select(Study, D1, D2, D3, D4, D5, D6)

q2_rob_trafficlight <- rob_traffic_light(data = q2_plot_ds,
                                                    tool = "Generic",
                                                    psize = 10,
                                                    overall = FALSE)

p8 <- q2_rob_trafficlight +
  ggplot2::labs(
    caption = "
    Domains:
  D1: Representativeness of the sample (selection bias)
  D2: Characteristics of non-respondents (selection bias)
  D3: Symptom assessment (information bias)
  D4: Recording of symptoms (information bias)
  D5: Classification of asymptomatic status (misclassification bias)
  D6: Selective reporting of symptoms status (attrition bias)")

p8 <- p8 + 
  ggplot2::ggtitle("Question 2.1") +
  theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size = 16, face = "bold"))

dev.new()
png("q2_new.png", width = 1000, height = 300)
p8
graphics.off()

@@

![ROB Q1_1](q1_1_new.png)
![ROB Q1_1](q1_2_new.png)
![ROB Q1_1](q2_new.png)
